{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-21 bmvc_review.tex
Final Adjustments

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate metrics to compare the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high},
MOSSE \cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast} and ones in relatively
lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny\:\:\:\:\:\:\textbf{UAV123}\hspace{.44\linewidth}\:\:\:\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

@@

\textbf{Performance on UAV123$\_$10fps Dataset.} It maybe a slight
digression from the main idea -- the idea of deploying multiple KCFs
to make a very fast and effective, single target tracking
available. We found that, with a slight modification, the proposed
method can effectively handle tracking of object in fast motion and in
large camera motion. Specifically we modified {\it E}nKCF by running
$R_{t}^{L}$ every frame and remove the particle filter instead. We
tested this modified {\it E}nKCF with another vision of the UAV123 that
the original dataset was temporally down-sampled at $10$ fps and makes
the challenging original dataset, because of objects in fast motion
and large ego-motion, more challenging. This is because the magnitude
of those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
compares the performance of the modified version of {\it E}nKCF and
other tracking methods. Our tracker outperforms other high-speed
correlation filter based trackers including KCF, DSST by about
$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
second in AUC while running about $150$ faster than the MUSTER
tracker.

>>>>

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate metrics to compare the performance of the proposed
algorithm with those of the state-of-the-art high speed tracking
algorithms. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high},
MOSSE \cite{bolme2010visual,henriques2015high}, and STC \cite{zhang2014fast} and ones in relatively
lower-speed ($\geq$50): SAMF \cite{li2014scale}, DSST
\cite{danelljan2014accurate}, Struck \cite{hare2012efficient}, MUSTER
\cite{hong2015multi}, TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels
precision. Three algorithms, SAMF, DSST, and Struck did about 5\%
better than ours in accuracy, but 10-20 times slower. For the scale
adaptation, {\it E}nKCF did second best in terms of AUC for the
success rate plot. It outperformed other tracking methods in
high-speed by about $20\%$-$25\%$ in AUC. In addition, it performed
even better than those algorithms that are slow, but a slightly better
in precision. For example, for AUC, {\it E}nKCF outperformed Struck
and DSST by $5\%$ and $10\%$ while running at more than $10$ and $30$
times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/pr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_uav123.eps}}
\bmvaHangBox{\includegraphics[width=3.00cm]{./figures/pr_otb100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/sr_otb100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

@@

\textbf{Performance on UAV123$\_$10fps Dataset} It maybe a slight
digression from the main idea -- the idea of deploying multiple KCFs
to make a very fast and effective, single target tracking
available. We found that, with a slight modification, the proposed
method can effectively handle tracking of object in fast motion and in
large camera motion. Specifically we modified {\it E}nKCF by running
$R_{t}^{L}$ every frame and remove the particle filter instead. We
tested this modified {\it E}nKCF with another vision of the UAV123 that
the original dataset was temporally down-sampled at $10$ fps and makes
the challenging original dataset, because of objects in fast motion
and large ego-motion, more challenging. This is because the magnitude
of those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
compares the performance of the modified version of {\it E}nKCF and
other tracking methods. Our tracker outperforms other high-speed
correlation filter based trackers including KCF, DSST by about
$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
second in AUC while running about $150$ faster than the MUSTER
tracker.
